\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{label} Autoren: Titel, Verlag, \url{http://...}, Datum.
\bibitem{ethereum-scale} Alyssa Hertig: How Will Ethereum Scale?, \url{https://www.coindesk.com/information/will-ethereum-scale}, accessed 20th of Mai 2019.
\bibitem{bitcoin-tps} Transactions Per Second (TPS): Cryptocurrency And Blockchain Importance Examined, \url{https://bitcoinexchangeguide.com/transactions-per-second-tps/}, 2nd of September 2018, accessed 20th of Mai 2019.
\bibitem{visa-tps} Jan Vermeulen: VisaNet - handling 100,000 transactions per minute, \url{https://mybroadband.co.za/news/security/190348-visanet-handling-100000-transactions-per-minute.html}, 17th of December 2016, accessed 20th of Mai 2019.
\bibitem{coordinator-part-1} IOTA Foundation: Coordinator. Part 1: The Path to Coordicide, \url{https://blog.iota.org/coordinator-part-1-the-path-to-coordicide-ee4148a8db08}, 20th of November 2018, accessed 20th of Mai 2019.
\bibitem{coordinator-part-2} IOTA Foundation: Coordinator. Part 2: IOTA is a DAG, not a Blockchain, \url{https://blog.iota.org/coordinator-part-2-iota-is-a-dag-not-a-blockchain-2df8ec85200f}, 20th of November 2018, accessed 20th of Mai 2019.
\bibitem{coordinator-part-3} IOTA Foundation: Coordinator. Part 3: Approaches to Coordicide, \url{https://blog.iota.org/coordinator-part-3-approaches-to-coordicide-583fb82382bc}, 20th of November 2018, accessed 20th of Mai 2019.
\bibitem{coordinator-part-4} IOTA Foundation: Coordinator. Part 4: An Open Source Coordinator, \url{https://blog.iota.org/coordinator-part-4-an-open-source-coordinator-7d3804931058}, 20th of November 2018, accessed 20th of Mai 2019.
\bibitem{object-reputation-system} Kevin Walsh, Emin Guen Sirer: Experience with an Object Reputation System for Peer-to-Peer Filesharing, \url{https://www.usenix.org/legacy/event/nsdi06/tech/walsh/walsh.pdf}, accessed 20th of Mai 2019.
\bibitem{the-tangle} Serguei Popov: The Tangle - Version 1.4.3, \url{https://assets.ctfassets.net/r1dr6vzfxhev/2t4uxvsIqk0EUau6g2sw0g/45eae33637ca92f85dd9f4a3a218e1ec/iota1_4_3.pdf}, 30th of April 2018, accessed 20th of Mai 2019.
\bibitem{the-tangle-part-1} Alon Gal: The Tangle: an illustrated introduction, \url{https://blog.iota.org/the-tangle-an-illustrated-introduction-f359b8b2ec80}, 31st of January 2018, accessed 20th of Mai 2019.
\bibitem{the-tangle-part-2} Alon Gal: The Tangle: an illustrated introduction - Part 2: transaction rates, latency, and random walks, \url{https://blog.iota.org/the-tangle-an-illustrated-introduction-f359b8b2ec80}, 7th of February 2018, accessed 20th of Mai 2019.
\bibitem{the-tangle-part-3} Alon Gal: The Tangle: an illustrated introduction - Part 3: Cumulative weights and weighted random walks, \url{https://blog.iota.org/the-tangle-an-illustrated-introduction-f359b8b2ec80}, 14th of February 2018, accessed 20th of Mai 2019.
\bibitem{the-tangle-part-4} Alon Gal: The Tangle: an illustrated introduction - Part 4: Approvers, balances, and double-spends, \url{https://blog.iota.org/the-tangle-an-illustrated-introduction-f359b8b2ec80}, 21st of February 2018, accessed 20th of Mai 2019.
\bibitem{the-tangle-part-5} Alon Gal: The Tangle: an illustrated introduction - Part 5: Consensus, confirmation confidence, and the coordinator, \url{https://blog.iota.org/the-tangle-an-illustrated-introduction-f359b8b2ec80}, 28th of February 2018, accessed 20th of Mai 2019.
\bibitem{mcmc} Ben Shaver: A Zero-Math Introduction to Markov Chain Monte Carlo Methods, \url{https://towardsdatascience.com/a-zero-math-introduction-to-markov-chain-monte-carlo-methods-dcba889e0c50}, 22nd of December 2017, accessed 20th of Mai 2019.
\bibitem{poisson-process} Will Koehrsen: The Poisson Distribution and Poisson Process Explained, \url{https://towardsdatascience.com/the-poisson-distribution-and-poisson-process-explained-4e2cb17d459}, 21st of January 2019, accessed 20th of Mai 2019.
\bibitem{parasite-chain} Bartosz Kusmierz: Attack analysis - the simple parasite chain \url{https://blog.iota.org/attack-analysis-the-simple-parasite-chain-42a34bfeaf23}, 10th of October 2019, accessed 20th of Mai 2019.
\bibitem{label} Autoren: Titel, Verlag, \url{http://...}, Datum.


\end{thebibliography}

